### 2015-10-29 postdoctoral/gamma_functions.tex
whoops, that linear order doesn't induce the topology

  \begin{theorem}
    Let \(M\) be a LOTS with minimum \(0\).
    \(
      Z
        =
      \varprojlim^\star \{M, \nu, L\}
        \cong
      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
    \)
    where \(M'=M\setminus\{0\}\),
    \(\lexTimes\) induces the lexicographic ordering on the product,
    and \(-\infty\) is a least element.
  \end{theorem}

  \begin{proof}
    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
    \(\rho(\vect x)=\rho(\vect y)\)
    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

    Define \(r:Z\to \hat L\lexTimes M\)
    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.

    We first show that \(r\) is a bijection. Let \(A\) be left-closed
    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
    is similarly trivial.

    Finally let \(\vect 0<\vect x<\vect y\).
    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
  \end{proof}

  This gives us the previous result as a corollary:
  \(
    \varprojlim^\star \{2, \nu, L\}
      \cong
    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
      \cong
    \hat L
  \). Unfortunately, the result is not always compact.

  \begin{example}
    \(
      \varprojlim^\star \{I, \nu, I\}
        \cong
      \{-\infty\}\cup (0,1]\lexTimes(0,1]
    \)
  is not compact.
  \end{example}

  \begin{proof}
    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
    is closed discrete.
  \end{proof}

>>>>

  % \begin{theorem}
  %   Let \(M\) be a LOTS with minimum \(0\).
  %   \(
  %     Z
  %       =
  %     \varprojlim^\star \{M, \nu, L\}
  %       \cong
  %     \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
  %   \)
  %   where \(M'=M\setminus\{0\}\),
  %   \(\lexTimes\) induces the lexicographic ordering on the product,
  %   and \(-\infty\) is a least element.
  % \end{theorem}

  % \begin{proof}
  %   Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
  %   this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
  %   Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
  %   \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
  %   \(\rho(\vect x)=\rho(\vect y)\)
  %   and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

  %   Define \(r:Z\to \hat L\lexTimes M\)
  %   by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
  %   \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.

  %   We first show that \(r\) is a bijection. Let \(A\) be left-closed
  %   and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
  %   for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
  %   \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
  %   is similarly trivial.

  %   Finally let \(\vect 0<\vect x<\vect y\).
  %   If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
  %   Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
  %   for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
  % \end{proof}

  % This gives us the previous result as a corollary:
  % \(
  %   \varprojlim^\star \{2, \nu, L\}
  %     \cong
  %   \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
  %     \cong
  %   \hat L
  % \). Unfortunately, the result is not always compact.

  % \begin{example}
  %   \(
  %     \varprojlim^\star \{I, \nu, I\}
  %       \cong
  %     \{-\infty\}\cup (0,1]\lexTimes(0,1]
  %   \)
  % is not compact.
  % \end{example}

  % \begin{proof}
  %   The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
  %   is closed discrete.
  % \end{proof}
